---
title: "Project 3: Visual Analysis of Youth Literacy Rates and Annual Percent of GDP Spent on Education"
output: html_document
---


#### This html page, produced by creating an R markdown document, and using KnitR to knit the file into html. The purpose of this html file, is to show our analysis of two different data sets. One data set is the youth literacy rate by countries for various years. The other data set is the percentage of a countries GDP spent on education for various years. This html also shows the steps required to reproduce our findings, given the same data. Given the variables in both data sets, we were able to query the data base in a few different ways, join the data to gather results, and visualize them using ggplot2. 



##### Rprofile.R:
An Rprofile.R document was created to include all of the packages required for the project, in order to avoid requiring packages in each of the R script files. Below is the call to the Rprofile document, and shows the necessary packages being loaded:


```{r}
source("../Rprofile.R", echo = FALSE)
```

#### Data:
Below is are the summary statistics for the data sets on Youth Literacy rate, and Annual percentage of GDP spent on education, as well as "head", which displays the first 6 items in the data sets.

```{r}
source("../01 Data/Project3.R", echo = TRUE)
```

#### Data Wrangling set 1 (Using inner-join):
Below is our first visualization of a subset of the data. The graph shows the Youth Literacy rates on the Y axis and the percentage of GDP spending on education on the X axis. We started with this graph to get an idea of the overall correlation for all of the countries, for all of the years. Most of the data we have is pre-2010, so that was chosen as the base year. The data shows a relatively low majorityof countries close to 100% literacy. It is hard to tell the effect of national spending on education for a possible number of reasons, so we will use the next few data visualizations to try analyze the trend.

```{r}
source("../02 Data Wrangling/Plot1.R", echo = TRUE)
```

#### Data Wrangling set 2 (Using outer-join):
Below a visualization of a subset of the data. For this visualization, we wanted to observe the correlaton between government education spending and youth literacy rates in some developing African countries. Although there exists a few outliers in our data visualizations, it seems to be the trend for developing nations, that an increase in government spending on education is correlated with higher youth literacy rates. Our data visualization also shows the females in those developing countries often lagged behind in the literacy rates.

```{r}
source("../02 Data Wrangling/Plot2.R", echo = TRUE)
```

#### Data Wrangling set 3 (Using full-join):
Below is a visualization of a subset of the data. We thought it would be insightful to see how the variables changed over the time period between 2000 and 2012. As The faceted graph shows, there is a trickling of data points, representing countries, from the lower end of the graph to the upper end of the graph showing that literacy rates were improving through the years. It was surprising however to see that percentage of GDP spent on education seemed to play little role in the improvement of youth literacy rates over the years.

```{r}
source("../02 Data Wrangling/Plot3.R", echo = TRUE)
```

#### Data Wrangling set 4 :
An interesting variable we wanted to observe a little more closely was the gender variable. We assumed, specially in the developing countries, females would take a longer time to move up the literacy rates. The bar graph only represents countries with les then 50% youth literacy. As we can see from the data visualization, over time, there is much fewer male literacy rates below 50, while female literacy rates remain more prevalently under 50%.

```{r}
source("../02 Data Wrangling/Plot4.R", echo = TRUE)
```
